Providing better confidentiality and authentication on the Internet using Namecoin and MinimaLT

### 2013-12-24 paper.tex
Adding the triangle because it looks cool.
Blockchain

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance} 
\usepackage{url}

@@

\subsection{Squaring Zooko's triangle}
In this section, we are introducing Zooko's triangle conjecture and our attempt to square it.

>>>>

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance} 
\usepackage{url}
\usepackage{graphicx}

@@

\subsection{Zooko's triangle}
In this section, we are introducing Zooko's triangle conjecture and our attempt to square it.

\begin{figure}[h!]
\centering
\includegraphics[width=0.3\textwidth]{ZookoTriangle.png}
\end{figure}

Zooko's triangle says that out of these three properties \cite{zookoTriangleWikipedia}, you can usually take only two.
\begin{itemize}
\item \emph{Secure}\footnote{We can't agree with the naming of this property given the threat model we described previously in this paper.}: The quality that there is one, unique and specific entity to which the name maps.
\item \emph{Global}: The lack of a centralized authority for determining the meaning of a name. Instead, measures such as a Web of trust are used.
\item \emph{Memorable}: The quality of meaningfulness and memorability to the users of the naming system.
\end{itemize}

We can thus see that the systems proposed so far only gather two out of three of those properties. If we take the DNS(Sec) system with DANE extensions, we can have a memorable address that is "secure" but unfortunately doesn't have the global property because the ICANN is a centralized authority. Alternatively, Tor's Onion addresses do have the "secure" property and are global but a 16 character pseudorandom string is not memorable.

\subsection{Squaring Zooko's Triangle}

In the following section we are introducing a naming system that is an attempt at squaring Zooko's triangle.

Back in January 2011, Aaron Swartz described on his blog about how Bitcoin blockchain could help in squaring Zooko's triangle. A few months later, a first implementation of that idea came into existence, Namecoin.

\subsubsection{The Bitcoin Blockchain}

The blockchain is Bitcoin's main innovation. Blockchains are data-structures that were invented specifically for the Bitcoin project but they can be applied anywhere a distributed consensus needs to be established in the presence of malicious or untrustworthy actors. In this section we are going to write a small overview of the blockchain works.

Let's see how we can use the Bitcoin blockchain to register a domain name.
